---
title: "Schad et al (2020)に学ぶ名義尺度のコーディング"
subtitle: "Schad et al (2020)日本語注解"
author: "小川雅貴"
institute: "東京大学"
date: "2021/12/17 (updated: `r Sys.Date()`)"
output:
  #revealjs::revealjs_presentation:
  #  theme: "night"
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    #css: [ninjutsu]
    nature:
      ratio: 16:9
      #highlightStyle: github
      highlightStyle: magula
      highlightLanguage: r
      highlightLines: true
      highlightSpans: false
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false
        touch: true
        click: false
    includes:
      after_body: doc-creation/assets/remarkjs_extended.html
pdflink: "PDF files are currently unavailable"
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.path = "figures/",
  fig.width = 8,  #6
  fig.height = 6, #4
  fig.align = "center",
  fig.retina = 2,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "",
  cache = TRUE,
  cache.path = "cache/"
)
library(flipbookr)
```

class: middle center hide-slide-number


```{r, include = FALSE, cache = FALSE}
basename <- ifelse(exists("basename"), basename, "slide")
```


.info-box.w-50.bg-white.f3[
このHTMLスライドをご覧になる際は，
ChromeまたはFirefoxをお使いになることをお勧めいたします。
また，HTMLスライドの中身が正しく読み込まれない場合には，
ブラウザの更新ボタンを押して，再度スライドを読み込んでください。
なお，本スライドのPDF版は
<a href=`r rmarkdown::metadata$pdflink`>こちら<i class="fas fa-file-pdf"></i></a>
にございます。
]

<br>

.white[**右矢印➝**を押すと次のスライドに移ります]

---
class: inverse, middle, center


# 必要なパッケージ・関数の読み込み

<!-- get a flipbook version of the my_cars code chunk - pauses are where parentheses are balanced -->
---

`r chunk_reveal("load-packages-sources")`

```{r load-packages-sources, include = FALSE, eval = TRUE}
library(tidyverse)
library(lme4)
library(hypr)

# Rmarkdownをknitする際には，`source()`の項
# `local = knitr::knit_global()`
# を指定する
#
# https://bookdown.org/yihui/rmarkdown-cookbook/source-script.html
source(
  "http://read.psych.uni-potsdam.de/attachments/article/188/mixedDesign.v0.6.3.R",
  local = knitr::knit_global()
  )
#source("http://read.psych.uni-potsdam.de/pmr2/attachments/article/188/SchadEtAlJML2019.R")

# 乱数を固定する
set.seed(1)
```

---
class: inverse, middle, center

# Conceptual explanation of default contrasts (p.3)

---
class: inverse, middle, split-50


## Treatment contrast 処理対比

<!-- ^[以下，各対比の和訳は[R commanderにおける和訳](https://r-forge.r-project.org/scm/viewvc.php/pkg/po/R-ja.po?view=markup&revision=98&root=rcmdr&pathrev=235)に基づく] -->

::: columns

:::: pull-left

- 実験的介入treatmentの効果を，非介入群との比較で検討
  - 実験群 vs 統制群
- 各実験群を同一の統制群と比べる
--
- 例：様々なプライミング効果を，同一の統制群と比べる
    1. 音韻的プライミング
    2. 綴字プライミング
    3. プライミングなし（統制群）
--
  - 対比は次の2つ
      1. 音韻的プライミング vs プライミングなし（統制群）
      2. 綴字プライミング vs プライミングなし（統制群）

::::

:::: pull-right

```{r schema-treatment-contrasts, echo = FALSE}
demoData <- tribble(
  ~priming, ~rt,
  "control", 374,
  "phonological", 267,
  "orthographic", 304
) |>
mutate(
  diff.from.baseline = rt - first(rt)
)

#https://stackoverflow.com/questions/53553977/drawing-elements-arrows-circle-in-ggplot-r-to-show-the-difference-between

baseline <- demoData |>
  filter(priming == "control") |>
  dplyr::select(rt) |>
  pull()

demoData |>
  ggplot(
    aes(
      x = priming,
      y = rt
    )
  ) +
  geom_col() +
  geom_segment(
    aes(
      x = "control",
      y = baseline,
      xend = "control",
      yend = baseline + 100
    )
  ) +
  geom_segment(
    aes(
      x = "control",
      y = baseline + 100,
      xend = "orthographic",
      yend = baseline + 100
    )
  ) +
  geom_segment(
    aes(
      x = "orthographic",
      y = baseline + 100,
      xend = "orthographic",
      yend = demoData |>
        filter(priming == "orthographic") |>
        dplyr::select(rt) |>
        pull()
    ),
    arrow = arrow()
  ) +
  theme_bw()
```

::::

:::


---

```{r}
#M <- matrix(
#  c(0.8, 0.4),
#  nrow = 2,
#  ncol = 1,
#  byrow = FALSE
#  )

mixedDesign(
  B = 2,
  W = NULL,
  n = 5,
  M = matrix(
      c(0.8, 0.4),
      nrow = 2,
      ncol = 1,
      byrow = FALSE
    ),
  SD = 0.20,
  long = TRUE
  ) |>
  rename(F = B_A) |>
  mutate(
    F = case_when(
      F == "A1" ~ "F1",
      F == "A2" ~ "F2",
      TRUE ~ "NA_character_"
    )
  ) |>
  group_by(F) |>
  summarize(
    N = length(DV),
    M = mean(DV),
    SD = sd(DV),
    SE = SD/sqrt(N)
  ) |>
  (
    \(d){
      qplot(
        x = F, y = M,
        group = 1,
        data = d,
        geom = c("point", "line")
      )
    }
  )() +
  geom_errorbar(
    aes(
      max = M + SE,
      min = M - SE
    ),
    width = 0
  ) + 
  #scale_y_continuous(breaks=c(250,275,300)) + 
  labs(
    y = "Mean DV",
    x = "Factor F"
  )
```

---

# Hi!

--

This 'minimal flipbook' template has a couple of classic examples to get you building your first flipbooks!

--

flipbooks are code-movies.  The frames of the movies are slides. Here we use the R package {xaringan} to create a remark.js slideshow. 

--

Slide breaks are indicated with `---` (be careful trailing white space is not allowed)

--

flipbookr's `chunk_reveal()` disassembles a single code chunk and creates the "build" of multiple partial-code chunks on different slides (the --- is automatically generated for you too).  

--

We use `chunk_reveal()` it 'inline', not in a code chunk. 

--

Let's start!



---
class: inverse, middle, center


# First up: classic flipbook, using defaults to walk through code pipeline





<!-- get a flipbook version of the my_cars code chunk - pauses are where parentheses are balanced -->
---

`r chunk_reveal("my_cars")`

```{r my_cars, include = FALSE}
cars |>
  filter(speed > 4) |>
  ggplot() +
  aes(x = speed) + #BREAK
  aes(y = dist) + #BREAK
  geom_point(
    alpha = .8, 
    color = "blue" 
    ) + 
  aes(size = speed) #BREAK
```

---
class: inverse, center, middle


# Next up:  refer to same chunk, but use user defined breakpoints, and display output only






<!-- get another flipbook version of the my_cars code chunk, this time at the defined breaks and only showing output -->
---

`r chunk_reveal("my_cars", break_type = "user", display_type = "output", title = "### user defined break! using #BREAK message")`



---
class: inverse, center, middle

# Next up:  cycle through different lines of code





<!-- get flipbook that rotates through lines, my_fill -->
---

`r chunk_reveal("my_fill", break_type = "rotate", widths = c(1,1), title = "### cycle through lines of code marked #ROTATE")`

```{r my_fill, eval = F, echo = F}
ggplot(data = cars) +
  aes(x = speed) +
  aes(y = dist) +
  geom_point(
    size = 8,
    shape = 21,
    alpha = .9,
    color = "snow"
    ) +
  aes(fill = speed) +
  scale_fill_viridis_c(option = "magma") + #ROTATE
  scale_fill_viridis_c(option = "cividis") + #ROTATE
  scale_fill_viridis_c(option = "plasma") #ROTATE
```


---
class: inverse, center, middle

# Next up:  look at multiple realizations of same code





<!-- get flipbook that shows multiple realizations of the same code -->
---

`r chunk_reveal("cars_multi", break_type = 5, title = "### see multiple realizations of code")`

```{r cars_multi, include = FALSE}
cars |> 
  sample_frac(size = 1, replace = TRUE) |>      
  ggplot() +              
  aes(x = speed) +
  aes(y = dist) +
  geom_count(
    alpha = .7,
    color = "blue",
    size = 4
    ) + 
  geom_smooth(method = lm, se = FALSE) +
  coord_cartesian(xlim = range(cars$speed),
                  ylim = range(cars$dist)) +
  theme(legend.position = c(.9, .2))
```


---

<!-- adjust font size in this css code chunk, currently 80 -->

```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}

code.r.hljs.remark-code{
  position: relative;
  overflow-x: hidden;
}


code.r.hljs.remark-code:hover{
  overflow-x:visible;
  width: 500px;
  border-style: solid;
}

.highlight-last-item > ul > li, 
.highlight-last-item > ol > li {
  opacity: 0.5;
}

.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}

.column:first-of-type {float:left}
.column:last-of-type {float:right}

.split-30 .column:first-of-type {width: 30%}
.split-30 .column:last-of-type {width: 70%}
.split-40 .column:first-of-type {width: 40%}
.split-40 .column:last-of-type {width: 60%}
.split-50 .column:first-of-type {width: 50%}
.split-50 .column:last-of-type {width: 50%}
.split-60 .column:first-of-type {width: 60%}
.split-60 .column:last-of-type {width: 40%}
.split-70 .column:first-of-type {width: 70%}
.split-70 .column:last-of-type {width: 30%}

.pull-right + * {
  clear: both;
}

.pull-right + * {
  clear: both;
}
```
